---
title: "Validataion Set Flow Chart"
author: "Lauren Vanderlinden"
output: html_document
---

```{r, echo=FALSE, cache=FALSE, include=FALSE}
rm(list=ls())
options(stringAsFactors=FALSE)

library(GEOquery)
library(GEOsearch)
library(DBI)
library(RSQLite)
library(GEOmetadb)



```


### Goal ###

The overall goal of this report is to create a flow chart in how we selected the datasets for human validation for Joe's AR paper.  

```{r, echo=FALSE}

if(!file.exists('GEOmetadb.sqlite')) getSQLiteFile()
file.info('GEOmetadb.sqlite')
dbDisconnect(con)

results.1 = list()
cancerTypes = c("bladder", "breast", "colorectal", "lung", "prostate", "AML")

for(i in 1:length(cancerTypes)){
  results.1[[i]] = GEOSearchTerm(paste(cancerTypes[i], " cancer", sep=""))
}

bladder.1 =  GEOSearchTerm("bladder cancer")
bladder.2 = bladder.1[which(bladder.1$Organism=="Homo sapiens"),]
arraysWant = c("GPL6102", "GPL570", "GPL571")
bladder.3 = bladder.2[which(bladder.2$Platform %in% arraysWant),]
bladder.4 = bladder.3[which(bladder.3$Sample.Number>75),]


con <- dbConnect(SQLite(),'GEOmetadb.sqlite')
geo_tables <- dbListTables(con)
dbListFields(con,'gse')

breast.1 =  GEOSearchTerm("breast cancer")
colorectal.1 =  GEOSearchTerm("colorectal cancer")
prostate.1 =  GEOSearchTerm("prostate cancer")
lung.1 =  GEOSearchTerm("lung cancer")
aml.1 =  GEOSearchTerm("aml cancer")

